---
title: "Dots_Unique"
author: "Kelsey Moty"
date: "February 25, 2019"
output: html_document
---
Loading libraries
```{r setup,include=FALSE,}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(lubridate)
library(stringr)
library(geepack)
library(emmeans)
```

Loading in data file
```{r datasets, echo=FALSE, include=FALSE}
file <- here::here("02_experiment/expt2_unique/data", "Data_Dots_Unique_2.25.19.csv")

raw_data <- read_csv(file)
raw_data <- raw_data[,1:21]
colnames(raw_data) <- c("id", "dob", "dot", "age_cat", "condition", "order",  "square", "triangle", "star", "eye", "read", "hair", "pangolin", "quetzal", "tapir", "capybara", "jerboa", "fossa", "tarsier", "markhor", "numbat")

file <- here::here("02_experiment/expt2_unique/data", "dots_unique_demo.csv")
demographics <- read_csv(file)
colnames(demographics) <- c("id", "gender", "dob", "dot", "condition.order", "comments")
```

Merge demo and dataset
```{r combine, echo=FALSE}
dataset <- full_join(raw_data, demographics, by = "id")

# combining dob and dot data
dataset$dob.x <- ifelse(is.na(dataset$dob.x), dataset$dob.y, dataset$dob.x)
dataset$dot.x <- ifelse(is.na(dataset$dot.x), dataset$dot.y, dataset$dot.x)

# removing extraneous columns and renaming
dataset <- dataset %>% 
  dplyr::select(-c("dob.y", "dot.y")) %>% 
  dplyr::rename(dob = dob.x, dot = dot.x)
```

Renaming condition variables
```{r}
dataset <- dataset %>% 
  mutate(condition = dplyr::recode(condition, 
                                   `0` = "Baseline", 
                                   `1` = "Explanatory", 
                                   `2` = "Unique"))
```

Computing age
```{r}
dataset$dob <- mdy(dataset$dob)
dataset$dot <- mdy(dataset$dot)
dataset$age <- dataset$dot - dataset$dob
dataset$age_exact <- as.numeric(round(dataset$age/365.25, 2))
dataset$age_year <- abs(floor(dataset$age/365))

# merging age_cat and age_year
dataset$age_year <- ifelse(is.na(dataset$age_year), dataset$age_cat, dataset$age_year)

# removing unneeded age columns
dataset <- dataset %>% 
  select(-c("age_cat", "age"))

# removing 3-year-olds
dataset <- dataset[!(dataset$age_year == 3),]

# combining 6s and 7s
dataset$age_cat <- ifelse(dataset$age_year == 7, 6, dataset$age_year)
```

Removing dropped participants
```{r}
## TODO: go back to check why people were dropped

# in the dataset, some drops were marked by * listed with the condition
dataset <- dataset[!grepl("\\*", dataset$condition),]

# in the dataset, sometimes dropping participant was mentioned in the comments
dataset <- dataset[!grepl("(?i)drop", dataset$comments),]

# removing people with missing data
dataset <- dataset[grepl("*", dataset$pangolin),]
```

# Getting individual means
Here I am computing individual means for responses across the 9 animal trials. On individual trials, 3 = "all", 2 = "lots", 1 = "just some". Higher means mean participants had a higher tendency to respond "all" (or "lots"). Lower means mean participants had a higher tendency to respond "just some"
```{r, results=FALSE, warning=FALSE}
dataset <- dataset %>% 
  dplyr::mutate(age_cat = as.factor(age_cat)) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(average = mean(c(pangolin, quetzal, tapir, capybara, jerboa, 
                          fossa, tarsier, markhor, numbat)))
```

Computing means across conditions and ages
```{r, echo=FALSE}
data_means <- dataset %>% 
  dplyr::group_by(age_cat, condition) %>% 
  dplyr::summarize(mean = mean(average), 
         n = length(average)) 
                      
# Looking at means of across each animal
animal_means <- dataset %>% 
  dplyr::group_by(condition) %>%
  dplyr::summarise_all(funs(mean))
```

Creating long form of dataset to be used for the GEE analyses
```{r}
dataset_long <- dataset %>%
  select(id, condition, pangolin:numbat, age_cat, age_exact) %>% 
  gather(animal, response, -id, -condition, -age_cat, -age_exact) 
```

# Analyses
ANOVA comparing average response by age (here age is treated categorically) and condition (Baseline, Explanatory, and Unique)
```{r}
results <- aov(average ~ age_cat*condition, data = dataset)
summary(results)
```

Binomial gee for "all"" responses
Here a binary analysis makes more sense than a multinomial because even the responses are along three-point scale, kids are individually asked yes/no on any given trial. E.g., "Do you think all pangolins have XX" and kids respond yes or no. As opposed to asking kids "Do you think all, lots, or just some pangolins have XX"
```{r}
# converting data into binary for all
dataset_all <- dataset_long %>% 
    mutate(response = as.numeric(dplyr::recode(response, 
                                   `3` = "1", 
                                   `2` = "0", 
                                   `1` = "0")))

# GEE
results_all <- geeglm(response ~ age_cat + condition + age_cat*condition, 
                  data = dataset_all, 
                  family = binomial(logit), 
                  id = id, 
                  corstr = "exchangeable")
summary(results_all)

# To get Wald statistics from GEE
results_anova_all <- anova(results_all)
results_anova_all

# Pairwise comparisons across condition 
pairs(emmeans(results_all, ~ condition))
```

Binomial gee for lots
```{r}
# converting data into binary for lots
dataset_lots <- dataset_long %>% 
    mutate(response = as.numeric(dplyr::recode(response, 
                                   `3` = "0", 
                                   `2` = "1", 
                                   `1` = "0")))

# GEE
results_test_lots <- geeglm(response ~ age_cat + condition + age_cat*condition, 
                  data = dataset_lots, 
                  family = binomial(logit), 
                  id = id, 
                  corstr = "exchangeable")
summary(results_test_lots)

# To get Wald statistics from GEE
results_anova_lots <- anova(results_test_lots)
results_anova_lots

# Pairwise comparisons across condition 
pairs(emmeans(results_test_lots, ~ condition))
```

Binomial gee for just some
```{r}
# converting data into binary for some
dataset_some <- dataset_long %>% 
    mutate(response = as.numeric(dplyr::recode(response, 
                                   `3` = "0", 
                                   `2` = "0", 
                                   `1` = "1")))

# GEE
results_test_some <- geeglm(response ~ age_cat + condition + age_cat*condition, 
                  data = dataset_some, 
                  family = binomial(logit), 
                  id = id, 
                  corstr = "exchangeable")
summary(results_test_some)

# To get Wald statistics from GEE
results_anova_some <- anova(results_test_some)
results_anova_some

# Pairwise comparisons across age x condition 
pairs(emmeans(results_test_some, ~ age_cat|condition))
```


# Plots

This first plot is looking at children's average responses across conditions
```{r}
theme_set(theme_classic())

r1 <- ggplot(dataset, aes(factor(condition), average))
# 
# r1 + geom_boxplot(aes(color = factor(dataset$condition)),
#                   size = 1.5,
#                   fill = "#F6F6F6") + 
#   labs(x = "Condition",
#        y =" Average Response",
#        fill = element_blank()) +
#   theme(text         = element_text(size = 28),
#         axis.title.x = element_text(size = 32, 
#                                     face = "bold",
#                                     margin = margin(t = 20, r = 0, b = 0, l = 0)),
#         axis.title.y = element_text(size = 32, 
#                                     face = "bold",
#                                     margin = margin(t = 0, r = 20, b = 0, l = 0))) +
#   guides(color = FALSE) +
#   geom_point(data = dataset, 
#              aes(y = average, x = condition, color = factor(dataset$condition)),
#              position = position_jitter(w = 0.06, h = 0.02),
#              shape = 1,
#              size = 2)
# 
averages_violin <- r1 + geom_violin(scale = "width",
                 aes(fill = factor(dataset$condition)),
                 draw_quantiles = .5) +
  geom_point(data = dataset,
             aes(y = average, x = condition),
             position = position_jitter(w = 0.05, h = 0.02),
             shape = 1,
             size = 2) +
  labs(x = "Condition",
       y =" Average Response",
       fill = element_blank()) +
  theme(text         = element_text(size = 28),
        axis.title.x = element_text(size = 32,
                                    face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 32,
                                    face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0))) +
  guides(fill = FALSE)


# r <- ggplot() + 
#     geom_boxplot(data = dataset, 
#     aes(y = average, x = condition, color = factor(dataset$condition)),
#                   size = 1,
#                   fill = "#F6F6F6",
#     coef = 1.5,
#     outlier.size = 0) +
#   scale_y_continuous(expand = c(0, 0)
#                      ) +
#   coord_cartesian(ylim=c(.95,3.05)
#                   ) + 
#   labs(x = "Condition",
#        y =" Average Response",
#        title = " "
#        ) +
#   theme(text         = element_text(size = 28),
#         axis.title.x = element_text(size = 32, 
#                                     face = "bold",
#                                     margin = margin(t = 20, r = 0, b = 0, l = 0)),
#         axis.title.y = element_text(size = 32, 
#                                     face = "bold",
#                                     margin = margin(t = 0, r = 20, b = 0, l = 0))
#             ) +
#   geom_point(data = dataset, 
#              aes(y = average, x = condition, color = condition),
#              position = position_jitter(w = 0.05, h = 0.02),
#              shape = 1,
#              size = 2) + 
#   guides(color = FALSE)
averages_violin
```

This next plot looks at proportion of "all" "lots" and "just some" responses across conditions x age
```{r}
# computing proportions 
dataset_graph <- dataset_long %>% 
  dplyr::group_by(age_cat, condition, response) %>%
  dplyr::summarize(n = length(response)) %>% # getting counts by age and condition
  ungroup() %>% 
  dplyr::group_by(age_cat, condition) %>% 
  dplyr::mutate(n_total = sum(n), # getting total # participants across age and condition
                prop = n/n_total, # computing proportions of all, lots, and some responses across age x condition
                response = as.factor(response)) %>% 
  dplyr::ungroup() %>%
  dplyr::mutate(response = dplyr::recode(response,
                `1` = "Some",
                `2` = "Lots",
                `3` = "All"))

dataset_graph$response <- factor(dataset_graph$response, levels = c('All','Lots','Some'))

responses_stackedbar <- ggplot(dataset_graph, aes(x = age_cat,
                       y = prop, 
                       fill = response)) +
  geom_bar(stat = "identity") +
  facet_wrap( ~ condition) + 
  labs(x = "Age",
       y = "Proportion of responses",
       fill = element_blank()) +
  scale_y_continuous(expand = c(0, 0)) +
  theme(panel.grid.major = element_blank(),
        strip.background = element_blank(),
        axis.title.x = element_text(size = 32, face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 32, face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.text.x = element_text(size = 28),
        axis.text.y = element_text(size = 28),
        strip.text = element_text(size = 28),
        legend.text = element_text(size = 28)
        )
responses_stackedbar
```

This graph looks at proportions across animal trials 
```{r}
dataset_graph_animal <- dataset_long %>% 
  dplyr::group_by(animal, condition, response) %>%
  dplyr::summarize(n = length(response)) %>% 
  ungroup() %>% 
  dplyr::group_by(animal, condition) %>% 
  dplyr::mutate(n_total = sum(n),
                prop = n/n_total,
                response = as.factor(response))

dataset_graph_animal_baseline <- dataset_graph_animal %>% 
  filter(condition == "Baseline")

animal_stackedbar <- ggplot(dataset_graph_animal_baseline, aes(x = animal,
                       y = prop, 
                       fill = response)) +
  geom_bar(stat = "identity") +
  labs(x = "Age",
       y = "Proportion of responses",
       fill = element_blank()) +
  scale_y_continuous(expand = c(0, 0)) +
  theme(panel.grid.major = element_blank(),
        strip.background = element_blank(),
        axis.title.x = element_text(size = 32, face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 32, face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.text.x = element_text(size = 28),
        axis.text.y = element_text(size = 28),
        strip.text = element_text(size = 28),
        legend.text = element_text(size = 28)
        )
animal_stackedbar
```

proeprty stuff
```{r}
behavior <- c("dolphin", "bird", "rat", "tapir", "capybara", "jerboa")
temporary <- c("cat", "fish", "pig", "axolotl", "sundacolugo", "matamata")
color <- c("cow", "bear", "zebra", "quetzal", "fossa", "tarsier")
part <- c("deer", "giraffe", "dog", "pangolin", "markhor", "numbat")

dataset_long$property <- ifelse(dataset_long$animal %in% behavior, "behavior",
                                ifelse(dataset_long$animal %in% temporary, "temporary",
                                       ifelse(dataset_long$animal %in% color, "color", 
                                              ifelse(dataset_long$animal %in% part, "part", "NA")))) 
```

```{r}
dataset_unfamiliar_plot_age <- dataset_long %>% 
  filter( age_cat != "35") %>% 
  dplyr::mutate(response_all = ifelse(response == 3, 1, 0),
                response_lots = ifelse(response == 2, 1, 0),
                response_some = ifelse(response == 1, 1, 0)) %>% 
  full_join(dataset_familiar_correct_child, by = "id") %>% 
  group_by(condition, property, age_cat) %>% 
  dplyr::mutate(prop_all = mean(response_all),
                prop_lots = mean(response_lots),
                prop_some = mean(response_some)) %>% 
  distinct(age_cat, condition, property, .keep_all = TRUE) %>% 
  select(age_cat, condition, property, prop_all, prop_lots, prop_some) %>% 
  gather(response_type, prop, -age_cat, -property, -condition) %>% 
  filter(!is.na(age_cat)) %>% 
  mutate(response_type = gsub("prop_", "", response_type))

property_stackedbar_age <- ggplot(dataset_unfamiliar_plot_age, 
                       aes(x = property,
                           y = prop, 
                           fill = response_type)) +
  geom_bar(stat = "identity") +
  facet_grid( . ~ condition,
              drop = TRUE) + 
  theme_classic() + 
  labs(x = "Property Type",
       y = "Proportion of all, lots, and some responses",
       fill = element_blank()) +
  scale_y_continuous(expand = c(0, 0)) +
  theme(panel.grid.major = element_blank(),
        strip.background = element_blank(),
        axis.title.x = element_text(size = 14, face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        strip.text = element_text(size = 14),
        legend.text = element_text(size = 14)
        )
```


```{r}
# first creating a dataset for these analyses 
dataset_long_unfamiliar <- dataset_long %>% 
  dplyr::mutate(response_all = ifelse(response == 3, 1, 0), # coding binary variabile for all, lots, some for gee
                response_lots = ifelse(response == 2, 1, 0),
                response_some = ifelse(response == 1, 1, 0)) %>% 
  group_by(id, property) %>% 
  dplyr::mutate(prop_all = mean(response_all), # getting proportion of all responses per kid per prop type
                prop_lots = mean(response_lots),
                prop_some = mean(response_some))
  
# also getting a separate dataset with just child participants
dataset_long_unfamiliar_child <- dataset_long_unfamiliar %>% 
  filter(age_cat != 35)

dataset_long_unfamiliar_child <- dataset_long_unfamiliar_child %>% 
  rename(cond = condition)
```

```{r}
# age treated categorically
property_type <- lm(response ~ cond + property + cond*property + (1|id), 
                            data = dataset_long_unfamiliar_child)
anova(property_type)

#pairwise comparisons
pairs(emmeans(property_type,  ~ property|cond)) 
```

```{r}
# Gee of all responses by age and property type
property_all <- geeglm(response_all ~ cond + property + cond*property, 
                  data = dataset_long_unfamiliar_child, 
                  family = binomial(logit), 
                  id = id, 
                  corstr = "exchangeable")
summary(property_all)

# To get Wald statistics from GEE
property_anova_all <- anova(property_all)
property_anova_all

# pairwise compairons 
pairs(emmeans(property_all, ~ property)) 
```

```{r}
property_lots <- geeglm(response_lots ~ cond + property + cond*property, 
                  data = dataset_long_unfamiliar_child, 
                  family = binomial(logit), 
                  id = id, 
                  corstr = "exchangeable")
summary(property_lots)

# To get Wald statistics from GEE
property_anova_lots <- anova(property_lots)
property_anova_lots

# pairwise compairons 
pairs(emmeans(property_lots, ~ property)) 
```

```{r}
# Gee of all responses by age and property type
property_some <- geeglm(response_some ~ cond + property + cond*property, 
                  data = dataset_long_unfamiliar_child, 
                  family = binomial(logit), 
                  id = id, 
                  corstr = "exchangeable")
summary(property_some)

# To get Wald statistics from GEE
property_anova_some <- anova(property_some)
property_anova_some

# pairwise compairons 
pairs(emmeans(property_some, ~ property)) 
```

