---
title: "dots_unfamiliar"
author: "Kelsey Moty"
date: "February 25, 2019"
output: html_document
---

Loading the libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(lubridate)
library(stringr)
library(geepack)
library(emmeans)
```

Loading in data file
```{r datasets, echo=FALSE, include=FALSE}
file <- here::here("02_experiment/expt1_unfamiliar/data", "dots_unfamiliar_3.8.19.csv")

raw_data <- read_csv(file)
raw_data <- raw_data[,1:38]
colnames(raw_data) <- c("id", "gender", "dob", "dot", "age_exact", "age_cat", "condition", "order", "square", "triangle", "star", "eye", "read", "hair", "dolphin", "cat", "cow", "bear", "bird", "zebra", "deer", "giraffe", "fish", "pig", "mouse", "dog", "pangolin", "quetzal", "tapir", "capybara", "axolotl", "jerboa", "fossa", "tarsier", "sundacolugo", "markhor", "numbat", "matamata")
```

Computing exact age
```{r}
dataset <- raw_data

dataset$dob <- mdy(dataset$dob)
dataset$dot <- mdy(dataset$dot)
dataset$age <- dataset$dot - dataset$dob
dataset$age_exact <- ifelse(is.na(dataset$age_exact),
                            as.numeric(round(dataset$age/365.25, 2)), dataset$age_exact)
dataset$age_year <- abs(floor(dataset$age/365))

# merging age_cat and age_year
dataset$age_cat <- ifelse(is.na(dataset$age_cat), dataset$age_year, dataset$age_cat)

dataset <- dataset %>% 
  select(-age, -age_year)
```

Removing participants who aren't the right age
```{r}
# removing 3-year-olds or 8-year-olds
dataset <- dataset %>% 
  filter(!(age_cat == 3 | age_cat == 8)) 

# combining 6s and 7s
dataset$age_cat <- ifelse(dataset$age_cat == 7, 6, dataset$age_cat)
```

Getting individual means
Here I am computing individual means for responses across the 12 animal trials. On individual trials, 3 = "all", 2 = "lots", 1 = "just some". Higher means mean participants had a higher tendency to respond "all" (or "lots"). Lower means mean participants had a higher tendency to respond "just some"
```{r}
dataset <- dataset %>% 
  dplyr::mutate(age_cat = as.factor(age_cat)) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(
    average_fam = mean(c(dolphin, cat, cow, bear, bird, zebra, deer, giraffe, fish, pig, mouse, dog)),
    average_unf = mean(c(pangolin, quetzal, tapir, capybara, jerboa, 
                         fossa, tarsier, markhor, numbat, matamata, sundacolugo, axolotl)))

dataset_anova <- dataset %>% 
  select(id, age_exact, age_cat, order, average_fam, average_unf) %>% 
  gather(type, average, c(average_fam, average_unf))
```

Computing means across age and animal type
```{r}
data_means <- dataset_anova %>% 
  dplyr::group_by(age_cat, type) %>% 
  dplyr::summarize(mean = mean(average), 
         n = length(average)) 
```

Computing "correct" answer for familiar animal
Here I am looking at children's responses relative to adults' intuitions of variability for familiar animal categories. Whether a response was "correct" was determined by whether 1/3 of adults or more gave a particular response. For example, 1/3 of adults said "lots" for a particular animal and the other 2/3 of adults said "all", both "all" and "lots" would be considered correct responses. However, if fewer than 1/3 of adults said "lots", "lots" would no longer be a correct response

This specific code is determining which particular responses are correct
```{r}
dataset_correct <- dataset %>% 
  filter(age_cat == 35) %>% # filtering out just adults
  select(dolphin:dog) %>% # getting familiar animal trials
  gather(animal, response) %>% # converting to long format
  group_by(animal, response) %>%
  tally() %>% # tallying responses 
  mutate(prop = n/26) # computing proportion of responses adults gave by animal and response type

dataset_correct$correct <- ifelse(dataset_correct$prop > .33, "1", "0")
```

This code is checking to see on which trials participants had "correct" intuitions about variability within familiar animal categories
```{r}
# creating a long form of dataset
dataset_long <- dataset %>%
  gather(animal, response, -c(id:order, average_fam, average_unf)) 

# determining which of teh trials are familiar, unfamiliar, or practice
practice <- c("square", "triangle", "star", "hair", "read", "eye")
familiar <- c("dolphin", "cat", "cow", "bear", "bird", "zebra", "deer", "giraffe", "fish", "pig", "mouse", "dog")
unfamiliar <- c("pangolin", "quetzal", "tapir", "capybara", "axolotl", "jerboa", "fossa", "tarsier", "sundacolugo", "markhor", "numbat", "matamata")

dataset_long$type <- ifelse(dataset_long$animal %in% practice, "practice", 
  ifelse(dataset_long$animal %in% familiar, "familiar", "unfamiliar"))

# merging correct to long by animal and response: essentially this is creating a "correct" column
dataset_long <- full_join(dataset_long, dataset_correct)

# if correct column has an NA, assigning 0 because that mean kid did not get it correct
dataset_long$correct <- ifelse(dataset_long$type == "familiar" & is.na(dataset_long$correct), 0, dataset_long$correct)
```

Here, I am adding the property type associated with each animal trial. This will be used to look at children's responses relative to property type. 
```{r}
behavior <- c("dolphin", "bird", "rat", "tapir", "capybara", "jerboa")
temporary <- c("cat", "fish", "pig", "axolotl", "sundacolugo", "matamata")
color <- c("cow", "bear", "zebra", "quetzal", "fossa", "tarsier")
part <- c("deer", "giraffe", "dog", "pangolin", "markhor", "numbat")

dataset_long$property <- ifelse(dataset_long$animal %in% behavior, "behavior",
                                ifelse(dataset_long$animal %in% temporary, "temporary",
                                       ifelse(dataset_long$animal %in% color, "color", 
                                              ifelse(dataset_long$animal %in% part, "part", "NA")))) 
```


Plotting whether use of all lots and just some for familiar animals
```{r}
## TODO recreate this file using the raw data imported 
another_file <- here::here("02_experiment/expt1_unfamiliar/data", "familiar_response_avg_Dots-Unf.csv")

summary_data <- read_csv(another_file)

familiar_stackedbar <- ggplot(summary_data, aes(x = age,
                       y = average, 
                       fill = response)) +
  geom_bar(stat = "identity") +
  facet_wrap( ~ prevalence) + 
  labs(x = "Age",
       y = "Proportion of responses",
       fill = element_blank()) +
  scale_y_continuous(expand = c(0, 0)) +
  theme(panel.grid.major = element_blank(),
        strip.background = element_blank(),
        axis.title.x = element_text(size = 32, face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 32, face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.text.x = element_text(size = 28),
        axis.text.y = element_text(size = 28),
        strip.text = element_text(size = 28),
        legend.text = element_text(size = 28)
        )
familiar_stackedbar
```


Looking at proportion "correct" across age. First I do a regression where age is treated categorically because adults are included in the analyses. In the second regression, age is treated continuously
```{r}
# first need to filter out just familiar trials from dataset 
dataset_long_familiar <- dataset_long %>% 
  filter(type == "familiar") %>% 
  group_by(id) %>% 
  dplyr::mutate(correct_prop = mean(as.numeric(correct))) #computing individual proportion correct score

# # keeping only one row per participant
dataset_familiar <- dataset_long_familiar %>% 
    distinct(id, .keep_all = TRUE) 

# treating age categorically; testing children and adults
fit <- lm(correct_prop ~ age_cat, data = dataset_familiar)
anova(fit)

# pairwise comparison across age
pairs(emmeans(fit, ~ age_cat)) 

# now pulling out just children so we can do exact age 
dataset_familiar_child <- dataset_familiar %>% 
  filter(age_cat != 35)

# regression of correct by exact age
fit <- lm(correct_prop ~ age_exact, data = dataset_familiar_child)
anova(fit)

```

Plotting correct responses by exact age (adults are not included in this graph)
```{r}
plot_correct <- ggplot(
              data = dataset_familiar_child,
              aes(y = correct_prop, 
                  x = age_exact)) + 
  geom_point(
             position = position_jitter(w = 0, h = 0.1),
             size = 2,
             shape = 1,
             alpha = .4
  ) + 
  geom_smooth(
              method = lm,
              color = "black",
              fill = "#009E73"
  ) +
  scale_y_continuous(expand = c(0, 0)
  ) +
  coord_cartesian(ylim=c(0,1.1),
                  xlim=c(3.99,8)
  ) + 
  labs(x = "Age",
       y = "Participants' Responses"
  ) +
  theme(text         = element_text(size = 14),
        plot.title   = element_text(size = 14,
                                    face = "bold",
                                    hjust = .5),
        axis.title.x = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        strip.text = element_text(size = 12),
        strip.background = element_blank(),
        panel.border = element_rect(color = "black", fill = NA),
        panel.background = element_rect(fill = NA)
  ) + 
  guides(shape = FALSE)

plot_correct
```

I next pulled out the "correct" responses  for familiar animal where one of the correct responses wasn't "all". I did this because I wanted to test whether children were generally getting better at recognizing the real-world prevalence of properties across properties of all frequencies, or if specifically, children were getting better at recognizing the relative rarity of less frequent properties with age.

First, I create the dataset for this analysis
```{r}
# finding out which of the animals where "all" was a correct answer 
animal_all <- dataset_correct$animal[c(dataset_correct$response == 3 & dataset_correct$correct == 1)]

# creating dataset without these animals and recalculating proportion correct for reduced number of trials 
dataset_familiar_highvar <- dataset_long_familiar %>% 
  filter(!animal %in% animal_all) %>% # filtering out those animals from this dataset
  group_by(id) %>% 
  dplyr::mutate(correct_prop = mean(as.numeric(correct))) %>% # recalculating prop correct 
  distinct(id, .keep_all = TRUE) # keeping only one row per participant

# creating a dataset without adults
dataset_familiar_highvar_child <- dataset_familiar_highvar %>% 
  filter(age_cat != "35")
```

Next, I do two regressions 
```{r}
# treating age categorically; testing children and adults
fit <- lm(correct_prop ~ age_cat, data = dataset_familiar_highvar)
anova(fit)

# pairwise comparison of age
pairs(emmeans(fit, ~ age_cat)) 

# regression with just kids; age treated as continuous
fit <- lm(correct_prop ~ age_exact, data = dataset_familiar_highvar_child)
anova(fit)
```

Here, I plot correct across age for just these high variable properties
```{r}
plot_correct_high <- ggplot(
             data = dataset_familiar_highvar_child,
             aes(y = correct_prop, x = age_exact)) + 
  geom_point(
             position = position_jitter(w = 0, h = 0.1),
             size = 2,
             shape = 1,
             alpha = .4
  ) + 
  geom_smooth(
              method = lm,
              color = "black",
              fill = "#009E73"
  ) +
  scale_y_continuous(expand = c(0, 0)
  ) +
  coord_cartesian(ylim=c(0,1.1),
                  xlim=c(3.99,8)
  ) + 
  labs(x = "Age",
       y = "Participants' Responses"
  ) +
  theme(text         = element_text(size = 14),
        plot.title   = element_text(size = 14,
                                    face = "bold",
                                    hjust = .5),
        axis.title.x = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        strip.text = element_text(size = 12),
        strip.background = element_blank(),
        panel.border = element_rect(color = "black", fill = NA),
        panel.background = element_rect(fill = NA)
  ) + 
  guides(shape = FALSE)

plot_correct_high
```

Next, I check to see if age predicts correct responses for these low variable properties
```{r}
# creating dataset with low variable animals and recalculating proportion correct for reduced number of trials 
dataset_familiar_lowvar <- dataset_long %>% 
  filter(animal %in% animal_all) %>% # keeping the low variable animals in this dataset
  group_by(id) %>% 
  dplyr::mutate(correct_prop = mean(as.numeric(correct))) %>% # recalculating prop correct 
  distinct(id, .keep_all = TRUE) # keeping only one row per participant

# separate dataset for just kids
dataset_familiar_lowvar_child <- dataset_familiar_lowvar %>% 
  filter(age_cat != "35")
```


Next, I do two regressions looking at age predicting correct responses for these low variable animals
```{r}
# treating age categorically; testing children and adults
fit <- lm(correct_prop ~ age_cat, data = dataset_familiar_lowvar)
anova(fit)

# pairwise comparison of age
pairs(emmeans(fit, ~ age_cat)) 

# regression wih just kids
fit <- lm(correct_prop ~ age_exact, data = dataset_familiar_lowvar_child)
anova(fit)
```

# Graphing age for high variability animals
```{r}
plot_correct_low <- ggplot() + 
  geom_point(data = dataset_familiar_lowvar_child,
             aes(y = correct_prop, x = age_exact),
             position = position_jitter(w = 0, h = 0.1),
             size = 2,
             shape = 1,
             alpha = .4
  ) + 
  geom_smooth(data = dataset_familiar_lowvar_child,
              aes(y = correct_prop, x = age_exact),
              method = lm,
              color = "black",
              fill = "#009E73"
  ) +
  scale_y_continuous(expand = c(0, 0)
  ) +
  coord_cartesian(ylim=c(0,1.1),
                  xlim=c(3.99,8)
  ) + 
  labs(x = "Age",
       y = "Participants' Responses"
  ) +
  theme(text         = element_text(size = 14),
        plot.title   = element_text(size = 14,
                                    face = "bold",
                                    hjust = .5),
        axis.title.x = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        strip.text = element_text(size = 12),
        strip.background = element_blank(),
        panel.border = element_rect(color = "black", fill = NA),
        panel.background = element_rect(fill = NA)
  ) + 
  guides(shape = FALSE)

plot_correct_low
```

Next, I checked to see if knowledge of variability in familiar animals predicts expectations of variability in unfamiliar animals. First, I check using the proportion of correct with the full dataset, and then I check with the proportion of correct from the dataset with only those animals with these highly variable properties
```{r}
# Full dataset
# treating age categorically; testing children and adults
unfamiliar <- lm(average_unf ~ age_cat + correct_prop + age_cat*correct_prop, 
                      data = dataset_familiar)
anova(unfamiliar)

# pairwise comparison of age
pairs(emmeans(unfamiliar, ~ age_cat)) 

# age treated continuously
unfamiliar_child <- lm(average_unf ~ age_exact + correct_prop + age_exact*correct_prop, 
                            data = dataset_familiar_child)
anova(unfamiliar_child)

# Dataset with animals with highly variable properties 
# treating age categorically; testing children and adults
unfamiliar_highvar <- lm(average_unf ~ age_cat + correct_prop + age_cat*correct_prop, 
                         data = dataset_familiar_highvar)
anova(unfamiliar_highvar)

# pairwise comparison of age
pairs(emmeans(unfamiliar_highvar, ~ age_cat)) 

# age treated continuously
unfamiliar_highvar_child <- lm(average_unf ~ age_exact + correct_prop + correct_prop*age_exact, 
                               data = dataset_familiar_highvar_child)
anova(unfamiliar_highvar_child)

```

Here, I plot expectations of variability in unfamiliar categories. Here, I am using the dataset with only the high variable properties, but looks similar when using the full dataset
```{r}
plot_unfamiliar <- ggplot() + 
  geom_point(data = dataset_familiar_highvar_child,
             aes(y = average_unf, x = correct_prop),
             position = position_jitter(w = 0.03, h = 0.03),
             size = 2,
             shape = 1,
             alpha = .4
  ) + 
  geom_smooth(data = dataset_familiar_highvar_child,
              aes(y = average_unf, x = correct_prop),
              method = lm,
              color = "black",
              fill = "#009E73"
  ) +
  scale_y_reverse( lim=c(3.05,.95),
                   expand = c(0, 0),
                   breaks = c(1,1.5,2,2.5,3),
                   labels = c("3.0", "2.5", "2.0", "1.5", "1.0")
  ) +
  coord_cartesian(xlim=c(0,1)
  ) + 
  labs(x = "Knowledge of variability in familiar animals",
       y = "Expectations of variability in unfamiliar animals"
  ) +
  theme(text         = element_text(size = 14),
        plot.title   = element_text(size = 14,
                                    face = "bold",
                                    hjust = .5),
        axis.title.x = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        strip.text = element_text(size = 12),
        strip.background = element_blank(),
        panel.border = element_rect(color = "black", fill = NA),
        panel.background = element_rect(fill = NA)
  ) + 
  guides(shape = FALSE)

plot_unfamiliar
```

Now, I am looking at expectations of variability in unfamiliar animals depending on property types. Here, I am including a binary analysis of the data. This type of analysis makes more sense than a multinomial because even the responses are along three-point scale, kids are individually asked yes/no on any given trial. E.g., "Do you think all pangolins have XX" and kids respond yes or no. As opposed to asking kids "Do you think all, lots, or just some pangolins have XX"

First, I get the data prepped.
```{r}
# first creating a dataset for these analyses 
dataset_long_unfamiliar <- dataset_long %>% 
  filter(type == "unfamiliar") %>% # getting just the unfamiliar trials
  dplyr::mutate(response_all = ifelse(response == 3, 1, 0), # coding binary variabile for all, lots, some for gee
                response_lots = ifelse(response == 2, 1, 0),
                response_some = ifelse(response == 1, 1, 0)) %>% 
  group_by(id, property) %>% 
  dplyr::mutate(prop_all = mean(response_all), # getting proportion of all responses per kid per prop type
                prop_lots = mean(response_lots),
                prop_some = mean(response_some))
  
# also getting a separate dataset with just child participants
dataset_long_unfamiliar_child <- dataset_long_unfamiliar %>% 
  filter(age_cat != 35)

# adding correct prop for familiar 
dataset_long_unfamiliar_child <- dataset_familiar_highvar_child %>% 
  select(id, correct_prop) %>% 
  full_join(dataset_long_unfamiliar_child, by = "id")
```

Next, I run a regression where response is treated using a 3-point scale. 
```{r}
# age treated categorically
property_type <- lm(response ~ correct_prop + age_exact + property + correct_prop*property + correct_prop*age_exact + property*age_exact + property*age_exact*correct_prop + (1|id), 
                            data = dataset_long_unfamiliar_child)
anova(property_type)

#pairwise comparisons
pairs(emmeans(property_type, ~ property)) 
```

Then, I run the GEE's for the three response types. 
All responses:
```{r}

dataset_long_unfamiliar_child_noprop <- dataset_long_unfamiliar_child %>% 
  dplyr::group_by(id) %>% 
  dplyr::mutate(prop_all = sum(response_all)/12,
         prop_lots = sum(response_lots)/12,
         prop_some = sum(response_some)/12) 
# Gee of all responses by age and property type
property_all <- geeglm(response_all ~ correct_prop + age_exact + correct_prop*age_exact, 
                  data = dataset_long_unfamiliar_child_noprop, 
                  family = binomial(logit), 
                  id = id, 
                  corstr = "exchangeable")
summary(property_all)

# Gee of all responses by age and property type
property_all <- geeglm(response_some ~ age_exact * property + age_exact*property, 
                  data = dataset_long_unfamiliar_child, 
                  family = binomial(logit), 
                  id = id, 
                  corstr = "exchangeable")
summary(property_all)

# To get Wald statistics from GEE
property_anova_all <- anova(property_all)
property_anova_all

# pairwise compairons 
pairs(emmeans(property_all, ~ age_exact)) 
```

Lots responses: 
```{r}
# Gee of all responses by age and property type
property_lots <- geeglm(response_lots ~ correct_prop + property + correct_prop*property, 
                  data = dataset_long_unfamiliar_child, 
                  family = binomial(logit), 
                  id = id, 
                  corstr = "exchangeable")
summary(property_lots)

# To get Wald statistics from GEE
property_anova_lots <- anova(property_lots)
property_anova_lots

# pairwise compairons 
pairs(emmeans(property_lots, ~ property)) 
```

Just some responses:
```{r}
# Gee of all responses by age and property type
property_some <- geeglm(response_some ~ correct_prop + property + correct_prop*property, 
                  data = dataset_long_unfamiliar_child, 
                  family = binomial(logit), 
                  id = id, 
                  corstr = "exchangeable")
summary(property_some)

# To get Wald statistics from GEE
property_anova_some <- anova(property_some)
property_anova_some

# pairwise compairons 
pairs(emmeans(property_some, ~ property)) 
```

Plotting responses across property type
```{r}
# keeping only one row per participant
dataset_unfamiliar <- dataset_long_unfamiliar %>% 
    distinct(id, property, .keep_all = TRUE) %>% 
    mutate(age = ifelse(age_cat == 35, 9, age_exact))

dataset_unfamiliar_child <- dataset_long_unfamiliar_child %>% 
  distinct(id, property, .keep_all = TRUE)

dataset_unfamiliar_child_long <- dataset_unfamiliar_child %>% 
  gather(response_type, proportion, prop_all, prop_lots, prop_some) %>% 
  mutate(response_type = gsub("prop_", "", response_type))


property_plot_template <- function(p, r, q, s){
  ggplot(data = p, aes(x = r, y = q, color = s, fill = s)) +
  facet_grid(
    . ~ property
  ) +
  geom_point(
             position = position_jitter(w = 0.03, h = 0.03),
             size = 2,
             shape = 1,
             alpha = .4
  ) + 
  geom_smooth(
              method = lm,
              color = "black"
  ) +
  scale_y_continuous(expand = c(0, 0),
                     breaks = c(0, .33, .66, 1)
  ) +
  coord_cartesian(ylim=c(0,1),
                  xlim=c(0,1)
  ) + 
  scale_x_continuous(
    breaks = c(0, .25, .5, .75, 1),
    labels = c("0", "0.25", "0.5", "0.75", "1")
  ) +
  labs(x = "Knowledge of variability in familiar animal kinds",
       y = "Proportion of all, lots, and some responses"
  ) +
  theme(text         = element_text(size = 14),
        plot.title   = element_text(size = 14,
                                    face = "bold",
                                    hjust = .5),
        axis.title.x = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        strip.text = element_text(size = 12),
        strip.background = element_blank(),
        panel.border = element_rect(color = "black", fill = NA),
        panel.background = element_rect(fill = NA)
  ) + 
  guides(shape = FALSE,
         fill = FALSE,
         color = FALSE)
}

plot_continuous <- property_plot_template(dataset_unfamiliar_child_long,
                                   dataset_unfamiliar_child_long$correct_prop, 
                                   dataset_unfamiliar_child_long$proportion,
                                   dataset_unfamiliar_child_long$response_type)

dataset_unfamiliar_child_long_all <- dataset_unfamiliar_child_long %>% 
  filter(response_type == "all")

plot_all <- property_plot_template(dataset_unfamiliar_child_long_all,
                                   dataset_unfamiliar_child_long_all$correct_prop, 
                                   dataset_unfamiliar_child_long_all$proportion,
                                   dataset_unfamiliar_child_long_all$response_type)

plot_lots <- property_plot_template(dataset_unfamiliar_child,
                                    dataset_unfamiliar_child$age_exact, 
                                    dataset_unfamiliar_child$prop_lots)

plot_some <- property_plot_template(dataset_unfamiliar_child,
                                    dataset_unfamiliar_child$age_exact, 
                                    dataset_unfamiliar_child$prop_some)

dataset_familiar_correct_child <- dataset_familiar_child %>% 
  filter(age_cat != "35") %>% 
  select(id, correct_prop) %>% 
  distinct(id, correct_prop)

dataset_long$response <- ifelse(dataset_long$response == "0", 1, dataset_long$response)
dataset_unfamiliar_plot <- dataset_long %>% 
  filter(type == "unfamiliar", 
         age_cat != "35") %>% 
  dplyr::mutate(response_all = ifelse(response == 3, 1, 0),
                response_lots = ifelse(response == 2, 1, 0),
                response_some = ifelse(response == 1, 1, 0)) %>% 
  full_join(dataset_familiar_correct_child, by = "id") %>% 
  group_by(property, correct_prop) %>% 
  dplyr::mutate(prop_all = mean(response_all),
                prop_lots = mean(response_lots),
                prop_some = mean(response_some)) %>% 
  distinct(correct_prop, property, .keep_all = TRUE) %>% 
  select(correct_prop, property, prop_all, prop_lots, prop_some) %>% 
  gather(response_type, prop, -correct_prop, -property) %>% 
  mutate(response_type = gsub("prop_", "", response_type))


dataset_property_plot <- dataset_long %>% 
  filter(type == "unfamiliar", 
         age_cat != "35") %>% 
  dplyr::mutate(response_all = ifelse(response == 3, 1, 0),
                response_lots = ifelse(response == 2, 1, 0),
                response_some = ifelse(response == 1, 1, 0)) %>% 
  full_join(dataset_familiar_correct_child, by = "id") %>% 
  group_by(property, age_cat) %>% 
  dplyr::mutate(prop_all = mean(response_all),
                prop_lots = mean(response_lots),
                prop_some = mean(response_some)) %>% 
  distinct(property, age_cat, .keep_all = TRUE) %>% 
  select(property, age_cat, prop_all, prop_lots, prop_some) %>% 
  gather(response_type, prop, -property, -age_cat) %>% 
  mutate(response_type = gsub("prop_", "", response_type))
 
dataset_property_plot_individual <- dataset_long %>% 
  filter(type == "unfamiliar", 
         age_cat != "35") %>% 
  dplyr::mutate(response_all = ifelse(response == 3, 1, 0),
                response_lots = ifelse(response == 2, 1, 0),
                response_some = ifelse(response == 1, 1, 0)) %>% 
  full_join(dataset_familiar_correct_child, by = "id") %>% 
  group_by(id, property) %>% 
  dplyr::mutate(prop_all = mean(response_all),
                prop_lots = mean(response_lots),
                prop_some = mean(response_some)) %>% 
  distinct(id, property, .keep_all = TRUE) %>% 
  select(id, property, age_cat, prop_all, prop_lots, prop_some) %>% 
  gather(response_type, prop, -id, -property, -age_cat) %>% 
  mutate(response_type = gsub("prop_", "", response_type))
  

test <- summarySE(dataset_property_plot_individual, measurevar="prop", groupvars=c("property","response_type", "age_cat"))

test_all <- test %>% 
  filter(response_type == "all")
  
plot_property <- ggplot(test, 
                       aes(x = property,
                           y = prop,
                           color = response_type)) +
  facet_grid( . ~ age_cat ) +
  geom_point(size = 10) +
  geom_errorbar(aes(x = property, 
                    ymin = prop - se, 
                    ymax = prop + se), 
                width = .05
  ) +
  theme_classic() + 
  labs(x = "Property Type",
       y = "Proportion of all, lots, and some responses",
       fill = element_blank()) +
  scale_y_continuous(expand = c(0, 0),
                     breaks = c(0, .1, .2, .3, .4, .5),
                     labels = c("0%", "10%", "20%", "30%", "40%", "50%")) +
  coord_cartesian(ylim=c(0,1)) +
  theme(panel.grid.major = element_blank(),
        strip.background = element_blank(),
        axis.title.x = element_text(size = 14, face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        strip.text = element_text(size = 14),
        legend.text = element_text(size = 14)
        ) +
  guides(color = FALSE)

property_stackedbar <- ggplot(dataset_property_plot, 
                       aes(x = property,
                           y = prop, 
                           fill = response_type)) +
  geom_bar(stat = "identity") +
  theme_classic() + 
  labs(x = "Property Type",
       y = "Proportion of all, lots, and some responses",
       fill = element_blank()) +
  scale_y_continuous(expand = c(0, 0)) +
  coord_cartesian(ylim=c(0,1)) +
  theme(panel.grid.major = element_blank(),
        strip.background = element_blank(),
        axis.title.x = element_text(size = 14, face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        strip.text = element_text(size = 14),
        legend.text = element_text(size = 14)
        )

dataset_unfamiliar_plot_age <- dataset_long %>% 
  filter(type == "unfamiliar", 
         age_cat != "35") %>% 
  dplyr::mutate(response_all = ifelse(response == 3, 1, 0),
                response_lots = ifelse(response == 2, 1, 0),
                response_some = ifelse(response == 1, 1, 0)) %>% 
  full_join(dataset_familiar_correct_child, by = "id") %>% 
  group_by(property, age_cat) %>% 
  dplyr::mutate(prop_all = mean(response_all),
                prop_lots = mean(response_lots),
                prop_some = mean(response_some)) %>% 
  distinct(age_cat, property, .keep_all = TRUE) %>% 
  select(age_cat, property, prop_all, prop_lots, prop_some) %>% 
  gather(response_type, prop, -age_cat, -property) 

property_stackedbar_age <- ggplot(dataset_unfamiliar_plot_age, 
                       aes(x = age_cat,
                           y = prop, 
                           fill = response_type)) +
  geom_bar(stat = "identity") +
  facet_grid( . ~ property) + 
  theme_classic() + 
  labs(x = "Knowledge of property prevalence in familiar categories",
       y = "Proportion of all, lots, and some responses",
       fill = element_blank()) +
  scale_y_continuous(expand = c(0, 0)) +
  theme(panel.grid.major = element_blank(),
        strip.background = element_blank(),
        axis.title.x = element_text(size = 14, face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        strip.text = element_text(size = 14),
        legend.text = element_text(size = 14)
        )
```

temporary property breakdown
```{r}
dataset_temporary <- dataset_long %>% 
  filter(type == "unfamiliar", 
         age_cat != "35",
         property == "temporary") %>% 
  dplyr::mutate(response_all = ifelse(response == 3, 1, 0),
                response_lots = ifelse(response == 2, 1, 0),
                response_some = ifelse(response == 1, 1, 0)) %>% 
  full_join(dataset_familiar_correct_child, by = "id") %>% 
  group_by(animal) %>% 
  dplyr::mutate(prop_all = mean(response_all),
                prop_lots = mean(response_lots),
                prop_some = mean(response_some)) %>% 
  distinct(animal, .keep_all = TRUE) %>% 
  select(animal, prop_all, prop_lots, prop_some) %>% 
  gather(response_type, prop, -animal) %>% 
  mutate(response_type = gsub("prop_", "", response_type))

```


```{r}

plot_temporary <- ggplot(dataset_temporary, 
                       aes(x = animal,
                           y = prop,
                           color = response_type)) +
  # geom_count(data = dataset_property_plot_individual,
  #            position = position_jitter(w = .1, h = .025),
  #            alpha = .4) +
  geom_point(size = 10) +
  # geom_errorbar(aes(x = animal, 
  #                   ymin = prop - se, 
  #                   ymax = prop + se), 
  #               width = .05
  # ) +
  theme_classic() + 
  labs(x = "Property Type",
       y = "Proportion of all, lots, and some responses",
       fill = element_blank()) +
  scale_y_continuous(expand = c(0, 0),
                     breaks = c(0, .25, .5, .75, 1),
                     labels = c("0%", "25%", "50%", "75%", "100%")) +
  coord_cartesian(ylim=c(0,1)) +
  theme(panel.grid.major = element_blank(),
        strip.background = element_blank(),
        axis.title.x = element_text(size = 14, face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        strip.text = element_text(size = 14),
        legend.text = element_text(size = 14)
        ) +
  guides(color = FALSE)
```



This plot looks at proportion of all, lots, and just some responses by age (categorically) x property type
```{r}
property_stackedbar
```

Proportion of all responses by age (continuous); kid data only
```{r}
plot_all
```

Proportion of lots responses by age (continuous); kid data only
```{r}
plot_lots
```

Proportion of some responses by age (continuous); kid data only
```{r}
plot_some
```

Analyzing the practice trials
```{r}
dataset_practice <- dataset_long %>% 
  filter(type == "practice", age_cat != 35)

dataset_correct_plot <- dataset_familiar_highvar_child %>% 
  select(id, correct_prop)

test <- full_join(dataset_practice, dataset_correct_plot, by = "id") 

test$correct_group <- ifelse(test$correct_prop < .33, 0, 
                                ifelse(test$correct_prop > .75, 2, 1))

test$type <- ifelse(test$animal == "eye" | test$animal == "square", "all", 
                    ifelse(test$animal == "triangle" | test$animal == "read", "lots", "some"))

practice_means <- test %>% 
  dplyr::group_by(correct_group, type) %>% 
  dplyr::summarize(mean = mean(response), 
         n = length(response)) 


practice_stackedbar <- ggplot(test, 
                       aes(x = correct_prop,
                           y = type, 
                           color = type)) +
  geom_point(
    # shape = 1,
    size = 3,
    position = position_jitter(w = 0.05, h = 0.1)
    ) +
  theme_classic() + 
  labs(x = "Knowledge of property prevalence in familiar categories",
       y = "Proportion of all, lots, and some responses",
       fill = element_blank()) +
  scale_y_continuous(expand = c(0, 0),
                     breaks = c(1, 2, 3)) +
  theme(panel.grid.major = element_blank(),
        strip.background = element_blank(),
        axis.title.x = element_text(size = 22, face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 22, face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20),
        strip.text = element_text(size = 14),
        legend.text = element_text(size = 22)
        ) + 
  scale_color_manual(values=c("#D81B60", "#1E88E5", "#FFC107")) 

```


